Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-21 paper.tex
Text wrapping
Whitespace
Fix up first paragraph of XFOIL section

To help understand, and possibly predict, the $Re$-sensitivity on turbine
performance, a series of static foil coefficient datasets were computed with the
\hl {XFOIL (please define)} viscous panel method code \cite{Drela1989}, a commonly-used tool for
airfoil analysis, e.g., \cite{Castelli2011, Walker2014}, implemented as part of
the open source turbine design software QBlade \cite{Marten2013}. Simulations
were run for an angle of attack range of 0$^{\circ}$
 to 40$^{\circ}$, in increments of 0.5$^{\circ}$. Solver parameters used were 100 panels, a fixed speed, zero Mach
number, \texttt{NCrit = 9} %please check the use of \texttt here
 (default $\mathrm{e}^n$ transition criteria parameter
for an average wind tunnel) and no forced boundary layer transition.
Characteristics were computed for the approximate average blade chord Reynolds
numbers encountered in the tow tank experiments.

>>>>

% \texttt is used below since this is a software variable

To help understand, and possibly predict, the $Re$-sensitivity on turbine
performance, a series of static foil coefficient datasets were computed with the
viscous panel method code XFOIL \cite{Drela1989}, a commonly-used tool for
airfoil analysis, e.g., \cite{Castelli2011, Walker2014}, implemented as part of
the open source turbine design software QBlade \cite{Marten2013}. Simulations
were run for an angle of attack range of 0$^{\circ}$ to 40$^{\circ}$, in
increments of 0.5$^{\circ}$. Solver parameters used were 100 panels, a fixed
speed, zero Mach number, \texttt{NCrit = 9} (default $\mathrm{e}^n$ transition
criteria parameter for an average wind tunnel) and no forced boundary layer
transition. Characteristics were computed for the approximate average blade
chord Reynolds numbers encountered in the tow tank experiments.
